---
title: "Assignment 3 (Storytelling wirh Open Data)"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    social: menu
    source_code: embed
runtime: shiny
---

```{r setup, include=FALSE}
# List of libraries
library(shiny)
library(ggplot2)
library(GGally)
library(tidyverse)
```

Sidebar {.sidebar}
=======================================================================

### Analysis for "Video Games Sales Dataset"

Student Name: Rakyan Adhikara

Student ID: s3935019

GitHub Page: [Here](https://github.com/radhikara-rmit/videogamessales_analysis)

Dataset: [Video Games Sales Dataset](https://www.kaggle.com/datasets/sidtwr/videogames-sales-dataset)


```{r}
# Importing dataset
data <- read.csv("Video_Games_Sales_as_at_22_Dec_2016.csv")

# data pre-processing
data <- data %>% filter(Year_of_Release >= 2012)
data <- data %>% mutate(User_Popularity = if_else(User_Count >= 1000, "Popular", "Not Popular"))
data <- na.omit(data)
data$User_Score <- as.numeric(data$User_Score)
data$Year_of_Release <- as.numeric(data$Year_of_Release)
```

Explanation
=======================================================================

### Introduction

Video games are now such a commodity that people of all ages to enjoy. However, the market nowadays is relatively unchartered compared to other market. As such, some analyses for the critic scores and the User Scores would have many real-world uses. Example, small indie video game companies will know what are their best video game genres or platforms to create by using this predictive model. More importantly, we as customers can figure out if the critic scores and the User Score can be a great objective opinions of the games that we would like to buy in the future.

Thus, the main objective of this dashboard are analysis on User Scores, Critic Scores. 

Dataset is from Kaggle: https://www.kaggle.com/datasets/sidtwr/videogames-sales-dataset

### Dataset Features

Here are list of dataset features, the units and descriptions of each features:

  1. `Name` (**NA**): Name of the video game
  2. `Platform` (**NA**): Platform of the video game
  3. `Year_of_Release` (**yyyy**): Year of release of the video game
  4. `Genre` (**NA**): Genre of video game
  5. `Publisher` (**NA**): Publisher of video game
  6. `NA_Sales` (**USD, in millions**): Sales number of video game in North America
  7. `EU_Sales` (**USD, in millions**): Sales number of video game in Europe
  8. `JP_Sales` (**USD, in millions**): Sales number of video game in Japan
  9. `Other_Sales` (**USD, in millions**): Sales number of video game in other regions
  10. `Global_Sales` (**USD, in millions**): Sales number of video game globally
  11. `Critic_Score` (**NA**): Aggregate score compiled by Metacritic staff
  12. `Critic_Count` (**NA**): The number of critics
  13. `User_Score` (**NA**): Score by Metacritic's subscribers
  14. `User_Count` (**NA**): Number of users
  15. `Developer` (**NA**): Developer of the game
  16. `Rating` (**NA**): The ESRB ratings

Scores with platforms
=======================================================================

Row
-----------------------------------------------------------------------

### Box plot for user Scores for Video Games Platforms on Metacritic between 2012 and 2016

```{r}
data_criticscore <- with(data, reorder(Platform, -Critic_Score, median, na.rm=T))
data_ord_criticscore <- data
data_ord_criticscore$Platform <- factor(data_ord_criticscore$Platform,
                             levels = levels(data_criticscore))
plot1 <- ggplot(data_ord_criticscore, aes(x=Platform, y=Critic_Score, fill=User_Popularity)) + 
  geom_boxplot(width=0.5) + 
  labs(
    x = "Types of Video Games Platforms",
    y = "User Score on Metacritic (2012 - 2016)",
    fill = "Popularity"
  ) + 
  coord_flip() + 
  facet_wrap(~User_Popularity)
plot1
```

### Box plot for critic Scores for Video Games Platforms on Metacritic between 2012 and 2016

```{r}
data_userscore <- with(data, reorder(Platform, -User_Score, median, na.rm=T))
plot2 <- ggplot(data, aes(x=reorder(Platform, -User_Score), y=User_Score, fill=User_Popularity)) + 
  geom_boxplot(width=0.5) + 
  labs(
    x = "Types of Video Games Platforms",
    y = "Critic Score on Metacritic (2012 - 2016)",
    fill = "Popularity"
  ) + 
  coord_flip() + 
  facet_wrap(~User_Popularity)
plot2
```

Row
-----------------------------------------------------------------------

### Explanation

Based on the analysis above, it has been shown that based on the critic score (*sorted by the median*), the top 5 platforms in Metacritic between 2012 and 2016 are:

  1. **_XBOX_**
  2. _Nintendo DS_
  3. _GameBoy Advanced_
  4. _PC_
  5. _PlayStation 1_
  
and based on the user score (*sorted by the median*), the top 5 platforms in Metacritic between 2012 and 2016 are:

  1. **_PlayStation_**
  2. _GameBoy Advanced_
  3. _PlayStation 2_
  4. _Playstation Vita_
  5. _Nintendo DS_

Scores with global sales
=======================================================================

Row
-----------------------------------------------------------------------

### Scatter plot for user Scores for Video Games Platforms on Metacritic between 2012 and 2016

```{r}
plot3 <- ggplot(data, aes(x=Critic_Score, y=Global_Sales)) + 
  geom_point() + 
  labs(
    x = "Critic Score on Metacritic (2012 - 2016)",
    y = "Global Sales (in US$, millions)",
    fill = "Popularity"
  )
plot3
```

### Scatter plot for critic Scores for Video Games Platforms on Metacritic between 2012 and 2016

```{r}
plot4 <- ggplot(data, aes(x=User_Score, y=Global_Sales)) + 
  geom_point()+ 
  labs(
    x = "User Score on Metacritic (2012 - 2016)",
    y = "Global Sales (in US$, millions)",
    fill = "Popularity"
  )
plot4
```

Row
-----------------------------------------------------------------------

### Explanation

Based on the analysis above, it has been shown that there are some correlations between the global scales and both critic score and user score. However, both have weak correlation considering the slope of the scatterplot.

Here are some summary based on both scatterplots:

  1. Sales on a video game can reach above US$5 million if the critic score of it is above or around 75.
  2. More video games are being sold with:
    - The critic score between 50 and 100
    - The user score between 5.0 and 10.0
  3. The highest video game sales has the critic score of 97 with user score at 8.2
  3. The highest video game user score has the critic score of 83 with user score at 8.2 with global sales at US$0.09 million
  
```{r}
highest_sales_name <- data[which.max(data$Global_Sales),]$Name
highest_sales_global <- data[which.max(data$Global_Sales),]$Global_Sales
highest_sales_critic <- data[which.max(data$Global_Sales),]$Critic_Score
highest_sales_user <- data[which.max(data$Global_Sales),]$User_Score

paste("Game name:", highest_sales_name, ", Global sales:", highest_sales_global, ", Critic Score:", highest_sales_critic, ", User score:", highest_sales_user)

highest_user_name <- data[which.max(data$User_Score),]$Name
highest_user_global <- data[which.max(data$User_Score),]$Global_Sales
highest_user_critic <- data[which.max(data$User_Score),]$Critic_Score
highest_user_user <- data[which.max(data$User_Score),]$User_Score

paste("Game name:", highest_user_name, ", Global sales:", highest_user_global, ", Critic Score:", highest_user_critic, ", User score:", highest_user_user)
```

